Dependent Object Types

### 2012-06-30 doc/semester/report.tex
more patches

>>>>

\subsection{Functions as Sugar}\label{funsug}

We adopt Scala's model of treating functions as syntactic sugar for an
object with a special method. In order to do so, we introduce a new
kind of label for methods with one parameter: $m : S \tfun U$.

A difference in expressivity between this model and the original one
is that we now have to explicitly provide a return type of the method,
while the return type was inferred for functions. In practice, this is
cumbersome but not fundamentally limiting.

\subsection{Explicit Widening}\label{widening}

In the original DOT calculus, the \textsc{app} and \textsc{new} typing
rules have implicit relaxations. For instance, in \textsc{app}, the
argument type may be a subtypine of the declared parameter type. In
order to deal with all the soundness problems due to narrowing, we
make widening an explicit operation and changes those rules to be
strict by replacing those relaxed subtyping judgments with equality
judgments. Two types $S$ and $T$ are judged to be equal if $S <: T$
and $T <: S$.
